Computer Science House Constitution

### 2025-04-02 constitution.tex
Added spacing between sections

\asubsubsection{Prior Root Type Persons}
Prior RTPs are any members who were previously an RTP and are not currently on an extension given by the RTPs.
Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.

\asubsubsection{Renewal of a Root Type Person}
At the conclusion of each standard operating session, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
After each statement, an E-Board Vote, as described in \ref{Executive Board Vote} will be conducted to determine each candidate's continuation. 
Failure to secure the required majority vote will result in the RTP being required to resign their position.

>>>>

\asubsubsection{Prior Root Type Persons}
Prior RTPs are any members who were previously an RTP and are not currently an Active Member or on an extension given by the RTPs.
Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.

\asubsubsection{Renewal of a Root Type Person}
At the conclusion of each standard operating session, those intending to keep the rights and responsibilities of a current RTP must participate in a renewal process. 
During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
After each statement, an E-Board Vote, as described in \ref{Executive Board Vote}, will be conducted to determine each candidate's continuation. 
Failure to secure the required majority vote will result in the RTP being required to resign their position.
